CloneOverflow: \\ Discovery of Online Code Clones between \\Stackoverflow and Open Source Projects

### 2016-10-20 latex-acm/cloneoverflow.tex
Updates

\section{Introduction}
\begin{itemize}
	\item Definition of code clones, online code clones, pros \& cons
	\item Roles of Q\&A websites in supporting software development and education
	\item Problems of code reuse (bug propagation, licensing conflicts)
\end{itemize}

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clone between Stackoverflow and open source projects:} 
We manually investigate 2,371 clone pairs found between Java code fragments obtained from Stackoverflow accepted answers, and 63 Java open source projects.

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of reusing online code clones:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license. Moreover, out of 48 clones, there are 27 clones in Stackoverflow that are outdated and dangerous for being reused.

\section{Research Questions}
The study aims to answer the following research questions: \\ 
\textbf{RQ1 (online code clone):} \textit{How source code are reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale. \newline
\textbf{RQ2 (flow of online code clone):} \textit{what are the directions source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied. Is it from Q\&A site to open source projects, or the other way around, or both? \newline
\textbf{RQ3 (classification of online code clone):} \textit{How and why did these online code clone happen?} Can we categorise them? \newline
\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?

@@

\subsection{Dataset}
In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{QualitasCorpus}. We found that \textit{eclipse} project does not contain source code so we removed it from the dataset. This results in totally 63 projects being analysed. The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.

@@

\section{Results}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from another study \cite{Wang2013}. Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

@@

\begin{table*}[h]
	\centering
	\caption{Qualitas-\textit{O} (2013-09-01r) clone results}
	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
	\small
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{3}{*}{Statistics} 
			& \multicolumn{3}{c|}{Simian Default settings} 
			& \multicolumn{3}{c|}{Simian EvaClone settings}
			& \multicolumn{3}{c|}{NiCad Default settings} 
			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
			& \multicolumn{3}{c|}{792 fragments} 
			& \multicolumn{3}{c|}{1229 fragments}  
			& \multicolumn{3}{c|}{1141 fragments} 
			& \multicolumn{3}{c}{12400 fragments} \\ \cline{2-13}
			%& \multicolumn{3}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
			%& \multicolumn{3}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
			%& \multicolumn{3}{c|}{rename=none,abstract=none} 
			%& \multicolumn{3}{c}{rename=blind,abstract=literal} \\ %\cline{2-17}  
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
			\hline
			%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
			Total & 24,929 & -- & -- & 16,957,362 & --	& -- & 105,118 	& -- & -- & 113,557,298 & -- & -- \\
			Mean & 38 & 7.54 & 0.27 & 14,444 & 4.80 & 0.28 & 107 & 9.52 & 0.25 & 9,397 & 5.21 & 0.20 \\
			Std Dev. & 87 & 3.21 & 0.22 & 281,747 & 1.22 & 0.18 & 198 & 3.07 & 0.18 & 12,098 & 1.73 & 0.16 \\
			Max  & 551 & 49.00 & 0.94 & 9,599,676 & 18.00 & 0.89 & 1,792 & 39.00 & 0.80 & 227,077 & 44.00 & 0.86 \\
			Min  & 1 & 5.00 & 0.01 & 1 & 4.00 & 0.02 & 1 & 7.00 & 0.02 & 1 & 3.00 & 0.01 \\
			Median  & 3 & 7.00 & 0.23 & 22 & 5.00 & 0.24 & 15 & 8.00 & 0.19 & 6,105 & 5.00 	& 0.15 \\
			Mode  & 1 & 7.00 & 0.25 & 1 & 4.00 & 0.50 & 1 & 8.00 & 0.53 & 1 & 4.00 & 0.33 \\
			\hline
		\end{tabular} %
%	}
\end{table*}

\begin{table*}
	\centering
	\caption{Qualitas-\textit{N} (2016-08-05) clone results (44 new Qualitas projects)}
	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
	\small
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{3}{*}{Statistics} 
			& \multicolumn{3}{c|}{Simian Default settings} 
			& \multicolumn{3}{c|}{Simian EvaClone settings} 
			& \multicolumn{3}{c|}{NiCad Default settings} 
			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
			& \multicolumn{3}{c|}{707 fragments} 
			& \multicolumn{3}{c|}{1205 fragments} 
			& \multicolumn{3}{c|}{1068 fragments} 
			& \multicolumn{3}{c}{10231 fragments} \\  \cline{2-13}
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
			\hline
			Total & 60,536 & -- 	& -- 	& 22,797,190 & -- 	& --  & 648,165 & -- & -- & 573,438,528 & -- & -- \\ 
			Mean 	& 86 	& 7.37 	& 0.26 	& 18,919 	& 4.85 	& 0.28 & 607 & 9.39 & 0.25 & 47663 & 5.22 & 0.20 \\
			Std Dev. & 217 	& 2.22 	& 0.21 	& 326,588 	& 1.31 	& 0.19 & 1,499 & 2.98 & 1.81 & 58,833 & 2.77 & 0.15 \\
			Max 	& 1,298 & 32.00 & 0.94 & 11,127,286 & 21.00 & 0.92 & 10,550 & 36.00 & 0.84 & 1,246,598 & 250 & 0.96 \\
			Min 	& 1 	& 5.00 	& 0.01 	& 1 & 4.00 	& 0.02 & 1 & 7 & 0.02 & 1 & 2.00 & 0.01\\
			Median 	& 2 & 7.00 	& 0.21 	& 20		& 5.00 	& 0.25 & 33 & 8 & 0.19 & 52,077 & 5.00 & 0.15 \\
			Mode & 1 	& 7.00 	& 0.25 	& 1 		& 4.00 	& 0.50 & 1 & 8 & 0.67 & 1 & 4.00 & 0.33 \\
			\hline
		\end{tabular} %
	%}
\end{table*}

@@

			Projects & Old version & New versions & Latest change & Repo. & License & Notes \\

@@

\subsection{Agreement based clone pairs}

For agreement-based clone pairs, we use a threshold of 0.7 for both \textit{good} and \textit{ok}-match. A visualisation of \textit{good}-match common clone pairs between four sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}. There are 1,357 unique \textit{good}-match pairs. The distribution of 10,139 \textit{ok}-match pairs, which subsume the \textit{good}-match pairs, is depicted in Figure \ref{fig:venn4_orig_ok}.

Nevertheless,  NiCad produced renaming and clustering errors for some of the settings. This resulted in not all 63 projects had NiCad clone reports. For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors. For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvaClone}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs. \FIXME{Report the errors to NiCad creator.}

\FIXME{Maybe no longer needed?} We are interested in discovering reused code in the latest versions of Qualitas projects. So, we downloaded the newest release of each project and found 44 of them having newer updates. Then, we reran the experiment again on these 44 projects. Several projects triggered NiCad problem of clustering and renaming again as listed in Table \ref{tab:projects_missing}. The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria of this new dataset are also listed in Table \ref{t_agreed_good_clone_pairs}.

\begin{table*}
	\centering
	\caption{No.~of projects in Qualitas Original~(Qualitas-\textit{O}) and New (Qualitas-\textit{N}) successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{r|r|r|r|r|r}
		\hline
		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
		\hline
		Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvaClone}}}$ & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvaClone}}}$ \\ \hline
		63	& 57 & 46 & 44 & 40 & 34 \\
		\hline
		& \textit{6 clustering failed} & \textit{13 clustering failed} & & \textit{4 clustering failed} & \textit{6 clustering failed} \\
		& cayenne   & cayenne 	& & jboss (wildfly) & ArgoUML \\
		& checkstyle & checkstyle & & hadoop & checkstyle \\
		& db-derby 	& db-derby 	& & db-derby & db-derby \\
		& geotools 	& geotools  & & hibernate & cayenne \\
		& iReport 	& iReport   & & & jena \\
		& hibernate & ArgoUML 	& & & geotools \\
		&			& castor 		& & & \\
		&			& drjava 		& & & \\
		&			& ganttproject 	& & & \\
		&			& ivatagroupware & & &  \\
		&			& jasperreports & & & \\
		&			& jboss 		& & & \\
		&			& jchempaint 	& & & \\
		\hline
		& 			&  \textit{4 renaming failed} & & & \textit{4 renaming failed} \\
		&			& Vuze 		& & & Vuze \\
		&			& aspectj 	& & & hadoop \\
		&			& eXoPortal 	& & & jboss (wildfly) \\
		&			&  hibernate 	& & & hibernate \\
		\hline
	\end{tabular}
\end{table*}

\begin{table}
	\centering
	\caption{Distribution of agreement-based clone pairs reported using Bellon's criteria}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{Qualitas-\textit{O}} \\
		\hline
		Simian & NiCad & \textit{good}-match & \textit{ok}-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{default} & \textit{default} & 9 	& 473 \\ 
		\textit{default} & \textit{EvaClone} 	& 12 	& 353 \\ 
		\textit{EvaClone} 	& \textit{default} 	& 7 	& 60 \\
		\textit{EvaClone} 	& \textit{EvaClone} 	& 1,338 & 9528 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 \\
		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 \\
		\hline
	\end{tabular}
\end{table}

\begin{figure*}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
		\caption{\textit{good}-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
		\caption{\textit{ok}-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification_good_o}. We have manually investigated all of the 1,357 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.  However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.  According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{\textrm{\textit{EvaClone}}}$ produces a large number, 1,338, of false positive results (D, E, and F). Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs. There are totally 608 \textit{ok-match} pairs that were investigated. The 39 true positive pairs found are combinations of 8 unique Stackoverflow fragments, and 9 unique Qualitas Java files from 6 different projects.

@@

\begin{table*}
	\centering
	\caption{Qualitas-\textit{O}: Distribution of classification category A--F according to \textit{good}-match pairs}
	\label{tab:good_classification}
	\small
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{EvaClone}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{\textrm{\textit{EvaClone}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,319 & 1,338 \\
		\hline
		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1,320  & 1,366 \\
		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1,320  & 1,352 \\
		\hline
	\end{tabular} 
\end{table*}

\begin{table*}
	\centering
	\caption{Qualitas-\textit{O}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
	\label{tab:ok_classification}
	\small
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
		\hline
		Simian$_{df}$--NiCad$_{df}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
		Simian$_{df}$--NiCad$_{\textrm{\textit{EvaClone}}}$   									& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{df}$   									& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
		\hline
		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
		\hline
	\end{tabular} 
\end{table*}

>>>>

\section{Introduction}
\begin{itemize}
	\item Definition of code clones, online code clones, pros \& cons
	\item Problems of code reuse (bug propagation, licensing conflicts)
	\item Roles of Q\&A websites in supporting software development and education
\end{itemize}

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We processed 130,644,707 clone pairs and manually investigated 2,371 clone pairs between Java code fragments obtained from Stackoverflow accepted answers and 63 Java open source projects.

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and online Q\&A websites:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license. Moreover, out of 48 clones, there are 27 clones in Stackoverflow that are outdated and dangerous for being reused.

\section{Research Questions}
The study aims to answer the following research questions: \\ 
\textbf{RQ1 (online code clone):} \textit{To what extent  source code is reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale. \newline
\textbf{RQ2 (flow of online code clone):} \textit{what are the directions that source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied. Is it from Q\&A site to open source projects, or the other way around, or both? \newline
\textbf{RQ3 (classification of online code clone):} \textit{How do the online code clones happen?} What are the major causes creating the online code clones? \newline
\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?

@@

\subsection{Dataset}
In our study, we selected the latest version of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects. \textit{eclipse} project does not contain source code so it has been removed from the study resulting in totally 63 projects. The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.

@@

\section{Results}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from a study by Wang et al.~\cite{Wang2013}. %Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

\begin{table}[H]
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		%		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
		%		\hline
		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ % & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ \hline
		\hline
		\textit{Successful} & 63 & 63 & 57 & 46 \\ %& 44 & 40 & 34 \\
		\textit{Clust.~fail} & - & - & 6 & 13 \\
		\textit{Ren.~fail} & - &  - & 0 & 4 \\
		\hline
		%		& \textit{6 clustering failed} & \textit{13 clustering failed} \\ %& & \textit{4 clustering failed} & \textit{6 clustering failed} \\
		%		& cayenne   & cayenne 	\\ %& & jboss (wildfly) & ArgoUML \\
		%		& checkstyle & checkstyle \\ %& & hadoop & checkstyle \\
		%		& db-derby 	& db-derby 	\\ %& & db-derby & db-derby \\
		%		& geotools 	& geotools  \\ %& & hibernate & cayenne \\
		%		& iReport 	& iReport   \\ %& & & jena \\
		%		& hibernate & ArgoUML 	\\ %& & & geotools \\
		%		&			& castor 		\\ %& & & \\
		%		&			& drjava 		\\ %& & & \\
		%		&			& ganttproject 	\\ %& & & \\
		%		&			& ivatagroupware \\ %& & &  \\
		%		&			& jasperreports \\ %& & & \\
		%		&			& jboss 		\\ %& & & \\
		%		&			& jchempaint 	\\ %& & & \\
		%		\hline
		%		& 			&  \textit{4 renaming failed} \\ %& & & \textit{4 renaming failed} \\
		%		&			& Vuze 		\\ %& & & Vuze \\
		%		&			& aspectj 	\\ %& & & hadoop \\
		%		&			& eXoPortal 	\\ %& & & jboss (wildfly) \\
		%		&			&  hibernate 	\\ %& & & hibernate \\
		%		\hline
	\end{tabular}
\end{table}

@@

\begin{table*}[h]
	\centering
	\caption{Statistics of clones found between Stackoverflow and Qualitas projects using Simian and NiCad}
	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
	\small
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{3}{*}{Statistics} 
			& \multicolumn{3}{c|}{Simian$_{df}$} 
			& \multicolumn{3}{c|}{Simian$_{\textrm{\textit{EvCl}}}$}
			& \multicolumn{3}{c|}{NiCad$_{df}$} 
			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
			& \multicolumn{3}{c|}{792 fragments} 
			& \multicolumn{3}{c|}{1229 fragments}  
			& \multicolumn{3}{c|}{1141 fragments} 
			& \multicolumn{3}{c}{12400 fragments} \\ \cline{2-13}
			%& \multicolumn{3}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
			%& \multicolumn{3}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
			%& \multicolumn{3}{c|}{rename=none,abstract=none} 
			%& \multicolumn{3}{c}{rename=blind,abstract=literal} \\ %\cline{2-17}  
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
			\hline
			%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
			Total & 24,929 & -- & -- & 16,957,362 & --	& -- & 105,118 	& -- & -- & 113,557,298 & -- & -- \\
			Mean & 38 & 7.54 & 0.27 & 14,444 & 4.80 & 0.28 & 107 & 9.52 & 0.25 & 9,397 & 5.21 & 0.20 \\
			Std Dev. & 87 & 3.21 & 0.22 & 281,747 & 1.22 & 0.18 & 198 & 3.07 & 0.18 & 12,098 & 1.73 & 0.16 \\
			Max  & 551 & 49.00 & 0.94 & 9,599,676 & 18.00 & 0.89 & 1,792 & 39.00 & 0.80 & 227,077 & 44.00 & 0.86 \\
			Min  & 1 & 5.00 & 0.01 & 1 & 4.00 & 0.02 & 1 & 7.00 & 0.02 & 1 & 3.00 & 0.01 \\
			Median  & 3 & 7.00 & 0.23 & 22 & 5.00 & 0.24 & 15 & 8.00 & 0.19 & 6,105 & 5.00 	& 0.15 \\
			Mode  & 1 & 7.00 & 0.25 & 1 & 4.00 & 0.50 & 1 & 8.00 & 0.53 & 1 & 4.00 & 0.33 \\
			\hline
		\end{tabular} %
%	}
\end{table*}

%\begin{table*}
%	\centering
%	\caption{Qualitas-\textit{N} (2016-08-05) clone results (44 new Qualitas projects)}
%	\label{t_simian_raw_results}
%%	\resizebox{\columnwidth}{!}{%
%	\small
%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
%			\hline
%			\multirow{3}{*}{Statistics} 
%			& \multicolumn{3}{c|}{Simian Default settings} 
%			& \multicolumn{3}{c|}{Simian EvaClone settings} 
%			& \multicolumn{3}{c|}{NiCad Default settings} 
%			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
%			& \multicolumn{3}{c|}{707 fragments} 
%			& \multicolumn{3}{c|}{1205 fragments} 
%			& \multicolumn{3}{c|}{1068 fragments} 
%			& \multicolumn{3}{c}{10231 fragments} \\  \cline{2-13}
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
%			\hline
%			Total & 60,536 & -- 	& -- 	& 22,797,190 & -- 	& --  & 648,165 & -- & -- & 573,438,528 & -- & -- \\ 
%			Mean 	& 86 	& 7.37 	& 0.26 	& 18,919 	& 4.85 	& 0.28 & 607 & 9.39 & 0.25 & 47663 & 5.22 & 0.20 \\
%			Std Dev. & 217 	& 2.22 	& 0.21 	& 326,588 	& 1.31 	& 0.19 & 1,499 & 2.98 & 1.81 & 58,833 & 2.77 & 0.15 \\
%			Max 	& 1,298 & 32.00 & 0.94 & 11,127,286 & 21.00 & 0.92 & 10,550 & 36.00 & 0.84 & 1,246,598 & 250 & 0.96 \\
%			Min 	& 1 	& 5.00 	& 0.01 	& 1 & 4.00 	& 0.02 & 1 & 7 & 0.02 & 1 & 2.00 & 0.01\\
%			Median 	& 2 & 7.00 	& 0.21 	& 20		& 5.00 	& 0.25 & 33 & 8 & 0.19 & 52,077 & 5.00 & 0.15 \\
%			Mode & 1 	& 7.00 	& 0.25 	& 1 		& 4.00 	& 0.50 & 1 & 8 & 0.67 & 1 & 4.00 & 0.33 \\
%			\hline
%		\end{tabular} %
%	%}
%\end{table*}

@@

			Projects & Old version & New versions & Latest change & CVS & License & Notes \\

@@

\subsection{Agreement based clone pairs}
For agreement-based clone pairs, we use a threshold of 0.7 for both \textit{good} and \textit{ok}-match. A visualisation of \textit{good}-match common clone pairs between four sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}. There are 1,357 unique \textit{good}-match pairs. The distribution of 10,139 \textit{ok}-match pairs, which subsume the \textit{good}-match pairs, is depicted in Figure \ref{fig:venn4_orig_ok}.

Nevertheless,  NiCad produced renaming and clustering errors for some of the settings. This resulted in not all 63 projects had NiCad clone reports. For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors. For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvCl}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs. \FIXME{Report the errors to NiCad creator.}

%\FIXME{Maybe no longer needed?} We are interested in discovering reused code in the latest versions of Qualitas projects. So, we downloaded the newest release of each project and found 44 of them having newer updates. Then, we reran the experiment again on these 44 projects. Several projects triggered NiCad problem of clustering and renaming again as listed in Table \ref{tab:projects_missing}. The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria of this new dataset are also listed in Table \ref{t_agreed_good_clone_pairs}.

\begin{table}[H]
	\centering
	\caption{Distribution of agreement-based clone pairs reported using Bellon's criteria}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{Qualitas-\textit{O}} \\
		\hline
		Simian & NiCad & \textit{good}-match & \textit{ok}-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{default} & \textit{default} & 9 	& 473 \\ 
		\textit{default} & \textit{EvaClone} 	& 12 	& 353 \\ 
		\textit{EvaClone} 	& \textit{default} 	& 7 	& 60 \\
		\textit{EvaClone} 	& \textit{EvaClone} 	& 1,338 & 9528 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 \\
		\hline
		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
		\caption{\textit{good}-match(0.7) pairs}
		\label{fig:venn4_orig_good}
\end{figure}

\begin{figure}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
		\caption{\textit{ok}-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
\end{figure}

@@

The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification_good_o}. We have manually investigated all of the 1,357 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.  However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.  According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number, 1,338, of false positive results (D, E, and F). Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs. There are totally 608 \textit{ok-match} pairs that were investigated. The 39 true positive pairs found are combinations of 8 unique Stackoverflow fragments, and 9 unique Qualitas Java files from 6 different projects.

@@

\begin{table}
	\centering
	\caption{Distribution of classification category A--F according to \textit{good}- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
	\label{tab:good_classification}
	\small
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
		\hline
		\hline
		\multicolumn{9}{|c|}{\textit{good}-match pairs} \\
		\hline
		S$_{df}$--N$_{df}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
		S$_{\textrm{\textit{EvCl}}}$--N$_{\textrm{\textit{EvCl}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1319 & 1338 \\
		\hline
		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1320  & 1366 \\
		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1320  & 1352 \\
		\hline
		\hline 
%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
%		\hline
		\multicolumn{9}{|c|}{\textit{ok}-match pairs} \\
		\hline
		S$_{df}$--N$_{df}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   	& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   	& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
		\hline
		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
		\hline
	\end{tabular} 
\end{table}
